Adopting agile in the large: motivations, success factors and challenges

### 2014-01-08 journal/article.tex
Organizing research process chapter

The goal of the research was to aggregate evidence on how large organizations
transform into an agile way of working. The research was conducted as a
systematic litterature review, based on empirical studies.

@@

\item
RQ2: How do transformations proceed usually; do transformations exhibit patterns?

\item
RQ3: What are typical successes and challenges in an large scale agile
    transformation process?

@@

\subsection{Definition of large scale}

@@

We deviated from Kitchenham's guideline on the part of data extraction. Instead
of using data extraction forms we analyzed the primary studies by coding.

\subsubsection{Inclusion criteria}

Based on the research questions and intended focus of the research, we defined
three facets to guide any inclusion/exclusion decisions: agile software
engineering, focus on transformation, and large organizations. The first facet covers primary studies
focusing on software engineering organizations applying or striving to apply
agile methods. Examples on topics excluded by the first facet are agile
manufacturing, and applying Scrum practices in management boards. The second
facet states that included studies must provide insights relevant to
organizational transformation, and specifically to the research questions.
The third facet underlines the particular contribution we aim to provide with
this research, namely the exclusive focus on large organizations.

@@

- pitää olla systemaattinen
- pitää olla toistettava
==> Perustuu enimmäkseen siihen että on 2 tutkijaa toistamassa

There must be more discussion on transformation than a couple of sentences.
--> Esimerkkejä
--> Tasot 1--5 ??

Listing of not included topics. Discussion on these topics are considered not
providing insight to the research questions. Our goal is to address the research
questions, and specifically focus on analyzing the transformation process.
Not included topics:
--> Benefits of agile in general, problems with agile in general
--> Comparing agile and method X
--> Reporting on the current method, without consideration of how the method has
    been evolved (or transformed)
Tämän perusteella pitää siis kertoa itse prosessista: --> Kirjoita auki tämä
kriteeri paremmin.

Jos koko on epäselvä:
--> Tutkijat päättävät keskustelun ja kvalitatiivisen harkinnan perusteella
--> Tähän tarvitaan esimerkit, milloin on otettu mukaan, milloin on karsittu
    pois

--> Case ``only piloting'': Piloting cases that clearly span only one limited
    project are excluded. Especially if there is no discussion of the continuity
    of agile. See Scott 2008.

--> Cases must be empirical, i.e. present a real case. (Otherwise we would need
    to include textbooks also...)

--> Case of one agile team in an enterprise: This is unrelated if the single
    team has no effect on the rest of the enterprise. There is no
    ``organizational transformation'' if there is just one team soloing.

--> Transformation and ``scaling up'' are very closely related. In some cases
    they can not really be separated. For instance, if transformation begins
    with a pilot and spreads gradually through the organization, it is very
    likely that the process is seen as a ``scaling up'' journey.
    However, in general, we do not include discussions purely on scaling up,
    especially if no organizational change is considered.

@@

A database keyword search was chosen as the search strategy. Based on the
research questions three facets for keywords were chosen: agile software
development, organizational transformation, and large scale. Preliminary
searches showed however that picking keywords with good precision was very
difficult. As a result we excluded the third facet (large scale). Instead of
engineering the search terms, which proved to result in excluding some
relevant articles, we chose an approach of manually filtering the search
results. Still having a substantial part of the matches in the non-relevant  
areas such as agile manufacturing, we decided to limit searches to either be
included in major software publications or include the term ``software''. The
resulting facets and keywords are listed in Table \ref{table:searchterms}. The
databases included in the search are listed in Table \ref{table:databases}. All
databases supported searches using boolean search commands constructed from the
facets and keywords. The search yielded NNNN unique matches.

\begin{table}
    \begin{tabular}{ p{0.22\textwidth} p{0.76\textwidth} }
        \toprule
        Facet                  & Keywords   \\
        \midrule
        Agile methods\newline (before \& after) &
            agile, scrum, "extreme programming",\newline
            waterfall, "plan-driven", RUP \\
        Organizational transformation &
            transform*, transiti*, migrat*, journey, adopt*, deploy, introduc*,
            "roll-out", rollout \\
        Limit to software\newline related atricles &
            (software OR (conference="agile, xp, icgse, icse"))\newline
            NOT title+abs="manufacturing", conference="agile manufacturing"
        \\
        \bottomrule
    \end{tabular}
    \caption{Facets and related search terms used}
    \label{table:searchterms}
\end{table}

\begin{table}
    \begin{tabular}{ p{0.28\textwidth} l l }
        \toprule
        Database      & URL                     & N of matches   \\
        \midrule
        IEEExplore    & http://ieeexplore.ieee.org      & 745 \\ 
        ACM           & http://dl.acm.org               & 168 \\
        Scopus        & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge\newline(Thomson Reuters) &
        http://apps.webofknowledge.com & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search}
    \label{table:databases}
\end{table}

@@

Data extraction was implemented partially using data extraction forms, but also
by a iterative coding approach. (The reason was? ...). Questions for which the
answer was easy to trace (for example, organization size, time of
transformation, and RQ1 why are transformations initiated) were answered by
filling in a data extraction form. For the more complex research questions (RQ2
how does transformation usually proceed, RQ3 which are typical success factors
and challenges) the iterative coding approach was used. The iterative coding
approach...
--> Possibility to find many different viewpoinits for the research questions
--> Lots of items, which would have lead to much diversity in data extraction form

@@

>>>>

The goal of the research was to aggregate evidence on how large organizations
transform into an agile way of working. The research was conducted as a
systematic litterature review based on empirical studies.

@@

\item
RQ2: How do transformations usually proceed; do transformations exhibit patterns?

\item
RQ3: What are typical successes and challenges in a large scale agile
    transformation process?

@@

\subsection{Definition of large scale}
\label{sec:largescale}

@@

We deviated from Kitchenham's guideline on the part of data extraction. Instead
of using data extraction forms we analyzed the primary studies by coding. This
deviation was made in order to minimize how possible preconceptions would affect
the data extraction step, and to use a specialized software tool that allowed us
to record evidence in as much detail as possible.
% --> Possibility to find many different viewpoinits for the research questions
% --> Lots of items, which would have lead to much diversity in data extraction form

\subsubsection{Inclusion criteria}
\label{sec:inclusioncriteria}

Based on the research questions and intended focus of the research, we defined
three facets to guide any inclusion/exclusion decisions: agile software
engineering, focus on transformation, and large scale. The first facet
covers primary studies focusing on software engineering organizations applying
or striving to apply agile methods. The second facet states that included
studies must provide insights relevant to organizational transformation, and
specifically to the research questions. The third facet underlines the
particular contribution we aim to provide with this research, namely the
exclusive focus on large organizations. These three facets were used for
inclusion and exclusion in each study selection step, including search string
design, filtering by abstracts, and full text filtering.

Examples on topics excluded by the first facet are agile manufacturing, and
applying Scrum practices in management boards. In addition, we required that the
transformation was aimed to introduce agile methods into the studied
organization.

The facet of \emph{organizational transformation} was interpreted so that the
primary study presents insights on the process of transformation. Excluded
topics were: discussing a large agile effort but not presenting the how the
organization had evolved [ref?], pilot cases that clearly span one limited
project [Scott 2008?], and case studies that provide minimal information on the
transformation process [ref?].
--> Transformation and ``scaling up'' are very closely related. In some cases
    they can not really be separated. For instance, if transformation begins
    with a pilot and spreads gradually through the organization, it is very
    likely that the process is seen as a ``scaling up'' journey.
    However, in general, we do not include discussions purely on scaling up,
    especially if no organizational change is considered.

The facet of \emph{large scale} was interpreted as presented in section
\ref{sec:largescale}.
--> Case of one agile team in an enterprise: This is unrelated if the single
    team has no effect on the rest of the enterprise. There is no
    ``organizational transformation'' if there is just one team soloing.

In addition to the criteria listed above we excluded studies that were not
empirical. We excluded textbooks, studies presenting theories, and other studies
that did not include any case organization. We also excluded student experiments
as it is implausible to simulate the dynamics of a large organization in an
experiment.

@@

% - pitää olla systemaattinen
% - pitää olla toistettava
% ==> Perustuu enimmäkseen siihen että on 2 tutkijaa toistamassa
% 
% Jos koko on epäselvä:
% --> Tutkijat päättävät keskustelun ja kvalitatiivisen harkinnan perusteella
% --> Tähän tarvitaan esimerkit, milloin on otettu mukaan, milloin on karsittu
%     pois

-- snip --
Listing of not included topics. Discussion on these topics are considered not
providing insight to the research questions. Our goal is to address the research
questions, and specifically focus on analyzing the transformation process.
Not included topics:
--> Benefits of agile in general, problems with agile in general
--> Comparing agile and method X
--> Reporting on the current method, without consideration of how the method has
    been evolved (or transformed)
Tämän perusteella pitää siis kertoa itse prosessista: --> Kirjoita auki tämä
kriteeri paremmin.

\subsubsection{Preliminary searches}

Before proceeding with the keyword search a series of preliminary searches were
performed. Initial searches were made using keywords that were as general as
possible, including ``agile transformation'' and ``large scale agile''.
Additionally, a keyword search was done in the selected databases (listed in
table \ref{table:databases}) using the following search string:

\begin{verbatim}
((agil* OR scrum OR xp OR lean) AND
(transform* OR transit* OR change OR migrat*) AND
((large AND (scale OR organization))) OR enterprise)
\end{verbatim}

From these searches we compiled a list of 117 possibly relevant papers that
should be matched by the keyword searches. The keyword search came to include 75
of the preliminarily selected papers. The missed 32 preliminary papers were
separately examined for inclusion, resulting in including 3 additional papers as
primary studies.

@@

A keyword search in online databases was chosen as the search strategy. The
databases included in the search are listed in Table \ref{table:databases}. All
databases supported use of complex boolean logic in searches which allowed us
flexibility when constructing the search strings.

\begin{table}
    \begin{tabular}{ p{0.28\textwidth} l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. As a result we excluded the facet
\emph{large scale} from the keyword search, and relied on manual filtering.
Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we considered only articles including the term ``software'' or
articles published in relevant conferences. Instead of further engineering the
search terms, which proved to result in excluding some relevant articles, we
chose to manually filter the remaining search results. The resulting facets and
keywords are listed in Table \ref{table:searchterms}. The search yielded 1874
unique matches.

\begin{table}
    \begin{tabular}{ p{0.22\textwidth} p{0.76\textwidth} }
        \toprule
        Facet                  & Keywords   \\
        \midrule
        Agile methods\newline (before \& after) &
            \texttt{agile, scrum, "extreme programming",
            waterfall, "plan-driven", RUP}\\
        Organizational transformation &
            \texttt{transform*, transiti*, migrat*, journey, adopt*, deploy, introduc*,
            "roll-out", rollout}\\
        Only software\newline related atricles &
            \texttt{(software OR (conference="agile, xp, icgse, icse"))
            AND NOT (title+abs="manufacturing" OR conference="agile manufacturing")}
        \\
        \bottomrule
    \end{tabular}
    \caption{Facets and related search terms used}
    \label{table:searchterms}
\end{table}

\subsubsection{Study quality assessment}

@@

@@

\subsection{Limitations of research method}

-- A keyword search can not identify the facet of \emph{large scale}, and also
   \emph{transformation} is difficult to capture with keywords. Because of this
   we assume that it is likely that a some studies have been missed by the
   keyword search. As an improvement we would suggest combining the entire
   archive of \emph{Agile Conference} and \emph{Agile Processes in Software
   Engineering and Extreme Programming} to the results of the keyword search.
   These two conferences provided more than two thirds of the pimary sources.

-- Few of the primary studies presented a research method. Most of the studies
   were experience reports where the author was a member of the organization
   discussed. Because of this we must assume that the primary studies are
   biased. Due to this risk of bias we chose not to make statistical
   interpretations of the results.
